---
title: ElasticSearch bulk update and R
author: Iain Wallace
date: '2018-01-21'
slug: elasticsearch-and-r
categories: []
tags: []
---

### Aim

Test the bulk update feature of the wonderful elastic search package
https://github.com/ropensci/elastic/tree/bulk-update


## Install elastic search
I installed elastic search locally on my windows machine from the (Elastic Search website)[https://www.elastic.co/guide/en/elasticsearch/reference/current/windows.html] using all the default options.

After installation the server was available at http://localhost:9200/

## Install R packages
```{r warning=FALSE}
#install.packages("curl")
#devtools::install_github("ropensci/elastic@bulk-update")
```


## Set up index with data set

```{r warning=FALSE}
library(elastic)
library(tidyverse)

connect(es_port = 9200)

df <- data.frame(name = letters[1:3], size = 1:3, id = 100:102)

invisible(docs_bulk(df, 'foobar', 'foobar', es_ids = FALSE))


```

Index is available http://localhost:9200/foobar/foobar/101

## Test the update function

```{r test docs_bulk_update}
df2 <- data.frame(size = c(45, 56), id = 100:101)
df2

cat('before update')
Search("foobar", asdf = TRUE)$hits$hits

#(docs_bulk_update(df2, index = 'foobar', type = 'foobar'))
#Search("foobar", asdf = TRUE)$hits$hits

```

Error using the docs_bulk_update

docs_bulk_update(df2, index = 'foobar', type = 'foobar')

Error: could not find function "docs_bulk_update"