---
title: WIkiData and R
author: Iain Wallace
date: '2018-01-14'
slug: wikidata-and-r
categories:
  - R
  - chemical biology
tags:
  - data
  - sharing
---


[WikiData](https://www.wikidata.org/wiki/Wikidata:Main_Page) is a structured datasource that anyone can contribute to. The content of Wikidata is available under a free license, exported using standard formats, and can be interlinked to other open data sets on the linked data web.

I am impressed in how useful it is for sharing scientific data in a structured manner *quickly*. WikiData provides a nice shortcut to standard mechanisms of sharing data. For example, a common workflow to create chemical biology datasets that link compounds to targets is for a curator to read interesting papers, extract data from the paper and then enter the data into a database. This introduces a significant lag from the publication of the data to the time that it is broadly accessible in machine readable format. 

Some examples of wonderful resources that are created in this manner

 * [Chembl](https://www.ebi.ac.uk/chembl/)
 * [Guide to Pharmacology](http://www.guidetopharmacology.org/)
 
```{r}
library(WikidataQueryServiceR)

## Example query against WikiData
x<-query_wikidata('SELECT DISTINCT
  ?genre ?genreLabel
WHERE {
  ?film wdt:P31 wd:Q11424.
  ?film rdfs:label "The Cabin in the Woods"@en.
  ?film wdt:P136 ?genre.
  SERVICE wikibase:label { bd:serviceParam wikibase:language "en". }
}')

```


The wikidata community is **very** welcoming. There is page to request queries [here]().

Within 24hrs of posting a question on how to return all the chemical compounds in wikidat along with their chemcial structure, someone provided this statement.

```{r}

### return 
smiles_strings<-'SELECT DISTINCT ?compound ?compoundLabel ?canonical_smiles
   WHERE 
   {
    ?compound wdt:P233 ?canonical_smiles .
    SERVICE wikibase:label { bd:serviceParam wikibase:language "en". }
   }
'

```


